%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure generated PDF is machine-readable / ATS-parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=-0.5pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Lukas Müller} \\ \vspace{1pt}
    \small Frankfurt am Main, Germany $|$
    \href{mailto:contact@lukasmueller.dev}{\underline{contact@lukasmueller.dev}} $|$
    \href{https://github.com/lbm2001}{\underline{GitHub}} $|$
    \href{https://www.linkedin.com/in/lukas-m-695b06195/}{\underline{LinkedIn}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Bachelor of Science in Computer Science}{Oct. 2023 -- Present}
      {Technical University of Darmstadt}{Darmstadt, HE}
      \resumeItemListStart
        \resumeItem{Current grade: 1.1 German scale (GPA: 3.9)}
        \resumeItem{Exchange semester: Aarhus University, Denmark, Jan. 2026 -- Jun. 2026}
        \resumeItem{Elective courses: Robot Learning, Visual Computing, Markov Decision Theory, Machine Learning in Game Theory}
      \resumeItemListEnd

    \resumeSubheading
      {Bachelor of Arts in Digital Business Management}{Oct. 2019 -- Sep. 2022}
      {Baden-Wuerttemberg Cooperative State University}{Mannheim, BW}
      \resumeItemListStart
        \resumeItem{Final grade: 1.2 German scale (GPA: 3.8)}
        \resumeItem{Thesis: Conception of a Strategy to Increase Data Quality for a Predictive Analytics Application}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Working Student Machine Learning \& Data Engineering}{Aug. 2024 -- Present}
      {Compredict GmbH}{Darmstadt, HE}
      \resumeItemListStart
      \resumeItem{Implemented a contrastive timestamp-embedding model in Keras and integrated it into a production Python package for time-series analysis and visualization}
      \resumeItem{Developed Python packages for data quality and data labeling for high-frequency time-series data, including core logic, tests, and documentation}
    \resumeItem{Built unit and integration tests for data pipelines in MWAA and FastAPI services to improve reliability of ML systems}
      \resumeItemListEnd

    \resumeSubheading
      {Working Student Bioinformatics Research \& Development}{Oct. 2022 -- Sep. 2023}
      {BioNTech SE}{Mainz, RP}
      \resumeItemListStart
        \resumeItem{Developed a data pipeline transferring local research files to AWS (S3/Glue/Redshift) and making them accessible in a data warehouse}
        \resumeItem{Extended a bioinformatics feature pipeline used for downstream machine learning workflows}
      \resumeItemListEnd

    \resumeSubheading
      {Cooperative Education Student}{Aug. 2019 -- Sep. 2022}
      {Fresenius Group}{Bad Homburg, HE}
      \resumeItemListStart
        \resumeItem{Completed internship rotations in Project Management, Business Intelligence, and Process Mining}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Cavitation Experiment Database (Team Project)}{Oct. 2025 -- Mar. 2026}
      {TU Darmstadt (Chair of Fluid Systems)}{}
      \resumeItemListStart
        \resumeItem{Built a TimescaleDB database replacing HDF5/JSON-based experimental data storage with a unified schema}
        \resumeItem{Developed a documented Python API for ingestion and querying of experimental sensor and metadata}
        \resumeItem{Set up unit/integration tests and GitLab CI/CD for linting, testing, and documentation deployment}
        \resumeItem{Technologies: Python, PostgreSQL, TimescaleDB, GitLab CI/CD}
      \resumeItemListEnd

    \resumeSubheading
      {MuJoPy}{Sep. 2025}
      {Open Source (GitHub/PyPI)}{}
      \resumeItemListStart
        \resumeItem{Built and published a Python package exposing MuJoCo models as robot graphs for ML workflows}
        \resumeItem{Implemented robot-graph feature extraction and a Pytest-based test suite}
        \resumeItem{Technologies: Python, MuJoCo, Pytest, PyPI}
      \resumeItemListEnd

\resumeSubheading
      {Large-Scale Robot Generation (Team Project)}{Apr. 2025 -- Sep. 2025}
      {Technical University of Darmstadt (Intelligent Autonomous Systems Group)}{}
      \resumeItemListStart
        \resumeItem{Built an MPNN-based variational autoencoder learning latent representations of robot morphologies in MuJoCo}
        \resumeItem{Implemented training and evaluation workflows in PyTorch with experiment tracking in Weights \& Biases}
        \resumeItem{Technologies: Python, PyTorch, MuJoCo, Weights \& Biases}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Programming}{: Python, SQL, C++, Java} \\
        \textbf{Data Engineering \& Backend}{: PostgreSQL, Apache Airflow/MWAA, FastAPI, AWS (Redshift/Glue/S3), Docker} \\
        \textbf{Machine Learning}{: PyTorch, TensorFlow, Keras, Weights \& Biases} \\
        \textbf{Testing \& Tooling}{: Pytest, GitLab CI/CD, Python packaging, Polars, Pandas} \\
        \textbf{Languages}{: German (native), English (fluent), Spanish (basic)}
    }}
  \end{itemize}
%-------------------------------------------
\end{document}